Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
Incomplete Results pass

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'', while
% AD stimulus
non-visual spatial perception is investigated using an annotation of
spatial references in the speech occurring in the movie's audio-description.
% GLM contrasts
We applied model-based, mass-univariate analyses to a series of datasets
with BOLD fMRI data from naturalistic and conventional block-design stimulation
from the same set of participants, available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.

@@

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlates with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses of the movie and the audio-description to results gained from a
traditional visual localizer \citep{sengupta2016extension}.
% individual level
On the level single subjects, we also assess the performance of the exclusively
auditory naturalistic stimulus as a substitute for a visual paradigm to localize
the PPA.
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
% reference to supplemental material
Results and discussion of the additional contrasts (PPA and negative controls)
can be found in the supplemental material

>>>>

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'', while
% AD stimulus
non-visual spatial perception is investigated using an annotation of
spatial references in the speech occurring in the movie's audio-description.
% GLM contrasts
We applied model-based, mass-univariate analyses to a series of datasets
with BOLD fMRI data from naturalistic and conventional block-design stimulation
from the same set of participants, available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
\todo{cite Häusler \& Hanke 2021}

@@

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlates with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compare results from whole-brain GLM
analyses of the movie and the audio-description to a
traditional visual localizer \citep{sengupta2016extension}.
% individual level
For each individual, we also compared the activation pattern from
naturalistic auditory stimulation to the individual PPA localization
with a block-design stimulus.
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
% reference to supplemental material
Results and discussion of the additional contrasts (PPA and negative controls)
can be found in the supplemental material. \todo{check if redundant with later refs}
